---
title: "summarize multiple alignment scores"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(magrittr)
source("functions.R")
```

This script aims to summerize the output scores of MstatX by sliding windows.
Given a set multiple alignments, MstatX compute the multiple alignment score of each site. 
The output of MstatX is a file contains 2 columns which specify the order of each site (1,2, ...) and the score of the corresponding site.

Given a fragment size, this script computes the scores of all fragments using a sliding window of that size. We can use these scores to spot out the most or the least varied region within the input sequences.

If the input sequences contain continuous sites (e.g gene)

```{r continuous sliding windows}
win <- 300
step <- 10
result <- intervalScore("score",win,step)
ggplot(data=result,aes(x=Start,y=Score)) +geom_line() + xlab("window start position") + ylab("Score") + ggtitle(paste0("window size = ",win,", step = ",step))
```


If the input sequences contain sites from discontinous positions (e.g snp), then a position file specifiying the chromosome name and the base position is required.

```{r position,warning=FALSE}
win=100000
step=10000
resultD <- positionScore("score_D_jensen.txt","position",win,step)
ggplot(data = resultD,aes(x=Start+win/2,y=Score)) + geom_bar(stat = "identity",width = win) + facet_wrap(~Chromosome,ncol=2,scales = "free_x") + xlab("Win Position") + ggtitle(paste0("Domestic - Win = ",win))+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

resultW <- positionScore("score_W_jensen.txt","position",win,step)
ggplot(data = resultW,aes(x=Start+win/2,y=Score)) + geom_bar(stat = "identity",width = win) + facet_wrap(~Chromosome,ncol=2,scales = "free_x") + xlab("Win Position") + ggtitle(paste0("Wild - Win = ",win))+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))

resultDiff <- resultD
resultDiff$Score <- resultW$Score-resultD$Score
ggplot(data = resultDiff,aes(x=Start+win/2,y=Score)) + geom_bar(stat = "identity",width = win) + facet_wrap(~Chromosome,ncol=2,scales = "free_x") + xlab("Win Position") + ggtitle(paste0("Difference - Win = ",win))+theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))
```

histogram distance
```{r}
pos <- read.table("position",header=FALSE)
colnames(pos) <- c("Chromosome","Position")
allChromosomes <- unique(pos$Chromosome)
dis <- c()
for (chr in allChromosomes){
  posChr <- dplyr::filter(pos,Chromosome==chr)
  posChr <- posChr[order(posChr$Position),]
  distChr <- posChr$Position[2:nrow(posChr)]-posChr$Position[1:(nrow(posChr)-1)]
  dis <- c(dis,distChr)
}
x<-hist(dis,breaks = 1000)
x$breaks[10]
```


